\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2011-05-05 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
added combineFeatures example in demo vignette
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@55274 bc3139a8-67e5-0310-9ffc-ced21a209358

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Section
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quantitation}

@@

@@

The results of figure 3 of \cite{Karp2010} are reproduced with 
the dummy experiment and show on figure \ref{fig:cv-plot}.

@@

\clearpage

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Section
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{From spectra to quantitative expression data}

\subsection{Reporter ions quantitation}\label{sec:quant}

@@

\subsection{Normalisation}\label{sec:norm}

@@

Figure 3 of \cite{Karp2010} is reproduced with 
the dummy experiment and show on figure \ref{fig:cv-plot}.

@@

\subsection{Feature aggregation}

The above quantitation and normalisation has been performed on quantitative data 
obtained from individual spectra. However, the biological unit of interest is not 
the spectrum but the peptide or the protein. As such, it is important to be able to 
summarise features that belong to a same group, i.e. spectra from one peptide, 
peptides that originate from one protein, or directly combine all spectra that have 
been uniquely associated to one protein.

\Rpackage{MSnbase} provides one function, \Rfunction{combineFeatures}, that allows 
to aggregate features stored in an \Robject{MSnSet} using build-in or user 
defined summary function and return a new \Robject{MSnSet} instance. 
The function has three main argument here described below. 
Additional details can be found in the function manual.

<<makeGroups1,echo=FALSE,cache=FALSE>>=
gb <- as.factor(fData(qnt)$precursor.mz)
@

\Rfunction{combineFeatures}'s first argument, \Robject{object}, is an instance of class \Robject{MSnSet}, 
as has been created in the section \ref{sec:quant} for instance. 
The second argument, \Robject{groupBy}, is a \Robject{factor} than has as many elements as 
there are features in the \Robject{MSnSet} \Robject{object} argument. The features corresponding 
to the \Robject{groupBy} levels will be aggregated so that the resulting \Robject{MSnSet} output 
will have \Rfunction{length(levels(groupBy))} features. Here, we will combine individual 
MSMS spectra based on their precursor mass-to-charge ratio. This information has been saved 
in the \Robject{MSnSet}'s \Robject{featureData} slot during the quantitation (see section \ref{sec:quant}). 
As shown below, this will result in \Sexpr{length(table(gb))} new aggregated features.

<<makeGroups2,echo=TRUE,cache=FALSE>>=
names(fData(qnt))
head(fData(qnt)$precursor.mz)
gb <- as.factor(fData(qnt)$precursor.mz)
table(gb)
@

The third argument, \Robject{fun}, 
defined how to combine the features. Predefined functions are readily available and can be 
specified as strings 
(\Robject{fun="mean"}, \Robject{fun="median"}, \Robject{fun="sum"}, 
\Robject{fun="weigthed.mean"} or \Robject{fun="medianpolish"} to compute respectively the mean, 
media, sum, weighted mean or median polish of the features to be aggregated). 
Alternatively, is is possible to supply userdefined functions with 
\Robject{fun=function(x) \{ ... \}}. We will use the \Robject{median} here.

<<combineFeatures,echo=TRUE,cache=FALSE>>=
qnt2 <- combineFeatures(qnt,groupBy=gb,fun="median")
qnt2
@

Other intended ways to define aggregation groups is to import 
identification data into R and collate it to the \Robject{MSnSet} 
feature data, and subsequently use peptide sequences or protein assignments 
to combine features.
